Local Group Satellite Alignments

### 2017-08-09 paper/paper.tex
alignment bootstrap + normalized planes
updated plots in paper
plane fitting

\begin{figure*}
\centering
\includegraphics[width=0.31\textwidth]{mstar.pdf}
\includegraphics[width=0.31\textwidth]{vmax.pdf}
\includegraphics[width=0.31\textwidth]{nsat.pdf}
\caption{Basic characteristics for the 11 pairs selected to be Local
  Group Analogues (circles). From left to right: stellar mass, maximum circular
  velocity and number of bright ($M_V<-9$) satellites.
  Galaxy A is the galaxy with the higher stellar mass.
  The squares represent the same characteristics for the observed
  Local Group. 
\label{fig:general}}
\end{figure*}

@@

We fit satellite planes around each galaxy in the pair by randomly
generating 10000 unit vectors over the  sphere, each vector
representing the direction perpendicular to a plane passing through
the main galaxy's center of mass. 
We compute the dot product of the unit vector with the position vector
for each satellite, this scalar gives us the satellite distance to the
plane. 
The best plane is determined by the vector that gives the lowest
position satellite distance dispersion. 
We take the dispersion value as a measure of the plane's width.
For comparison we store the value and direction giving the
highest distance dispersion.
We denote by $\hat{p}$ the unit vector defining the direction
perpendicular to the best plane.

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{planes.pdf}
\caption{
Plane width as a function of the number of bright satellites.
Wider planes are expected as the satellite number increases.
\label{fig:planes}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{beta.pdf}
\caption{
Cumulative distribution for the gelocity anisotropy $\beta$.
\label{fig:beta}}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{mu_ri_cum.pdf}
\includegraphics[width=0.48\textwidth]{mu_ri_scatter.pdf}
\caption{
Cumulative distribution for the gelocity anisotropy $\beta$.
\label{fig:mu_ri}}
\end{figure*}

@@

%% http://adsabs.harvard.edu/abs/2017MNRAS.464.3825P
\end{document}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{mstar.pdf}
\includegraphics[width=0.30\textwidth]{vmax.pdf}
\includegraphics[width=0.30\textwidth]{nsat.pdf}
\caption{Basic characteristics for the 11 pairs selected to be Local
  Group Analogues (circles). From left to right: stellar mass, maximum circular
  velocity and number of bright ($M_V<-9$) satellites.
  Galaxy A is the galaxy with the higher stellar mass.
  The squares represent the same characteristics for the observed
  Local Group. 
\label{fig:general}}
\end{figure*}

@@

We fit satellite planes around each galaxy in the pair by randomly
generating 10000 unit vectors homogeneously distributed over the
sphere.
Each vector represents the direction perpendicular to a plane passing through
the main galaxy's center of mass. 
We compute the dot product of this unit vector with the position vector
for each satellite, this gives us the satellite distances to the
plane. 
The best plane is determined by the vector that gives the lowest
sample standard deviation in the satellite distances to the plane.
In the set of unit vectors to be considered we also include the vector
$\hat{I}_a$, which provides the exact solution in the case of $3$
satallites. 
We take the sample standard deviation as a measure of the plane's width
and denote by $\hat{p}$ the unit vector defining the direction
perpendicular to the best plane.

@@

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{planes.pdf}
\includegraphics[width=0.48\textwidth]{planes_normalized.pdf}
\caption{
Plane width as a function of the number of bright satellites.
Wider planes are expected as the satellite number increases.
\label{fig:planes}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{beta.pdf}
\includegraphics[width=0.45\textwidth]{beta_scatter.pdf}
\caption{
Cumulative distribution for the gelocity anisotropy $\beta$.
\label{fig:beta}}
\end{figure*}

\begin{figure}
\includegraphics[width=0.45\textwidth]{mu_ip_scatter.pdf}
\includegraphics[width=0.45\textwidth]{mu_ri_scatter.pdf}
\includegraphics[width=0.45\textwidth]{mu_rp_scatter.pdf}
\centering
\caption{A}
\end{figure}

@@

%% http://adsabs.harvard.edu/abs/2017MNRAS.464.3825P

%M31 mass
%% https://arxiv.org/abs/1410.0017

%MW mass
%https://arxiv.org/abs/1407.1078

\end{document}
